Do return series have power-law tails with the same index?

### 2017-04-12 papers/FX/draft.tex
Revised the FX manuscript.

\subsection{Hill estimates of lower-tail scale parameters}\label{sec:HillScaleEstimates}
We assume the pure Pareto model \eqref{eq:3} with scale parameter $K>0$. 
Hill \cite{hill1975simple} proposed  the maximum-likelihood estimator of $K$
derived from the joint \ds\ of $k$ upper order statistics in the sample; cf.
Embrechts et al. \cite{embrechts:klueppelberg:mikosch:1997}, p.~334.
It is given by
\beao
\hat K_k = {k \over n} X_{(n-k+1)}\,.
\eeao
Estimates of $K$ {\red or $K^\alpha$?} of the ``Energy'', ``Consumer Staples'' and
``Information Technology'' sectors of the S\&P 500 index are computed
using this method. {\blue The results are shown in Figure~\ref{fig:sectors_parameters} {\red ???} along with estimates obtained
using the hybrid method described in section
\ref{sec:hybrid_estimation}.} {\red Figures of the Hill estimates of $K$ or $K^\alpha$ with Hill confidence bands. 
Discuss confidence bands and what you see in the data.}

%% Hence it is informative to test
%% the hypothesis that the tail indices of these return series are equal.
%% Hoga \cite{hoga:2016} devised tests suitable this purpose. We adopt his
%% approach but use our own implementation. The next section has more
%% details.

%% \subsection{Hill estimates of extreme quantiles}

@@

\subsection{Pareto-distributed returns}
We consider the case when $X$ has a two-sided Pareto \ds\ given by
\beam\label{eq:pareto}
  F_X(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \,,\\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0\,,
  \end{array}
  \right.
\eeam
where 
$\alpha, \beta > 1$, $0 < p < 1$ and $K,K' > 0$. Then we have
\beam\label{eq:xxie1.0}
 \wt u(F_X,\phi)\nonumber
  &=&
  \alpha\, K^\alpha\,  p\,
  \int_{-\infty}^0
  u\big( (1 - \phi) \ex^r + \phi \ex^x \big)\,
  {1 + b \over (K - x)^{\alpha + 1}} \,dx\\
    &&+
  \beta \,(K')^\beta\, (1 - p)
  \int_{0}^\infty
  u\big( (1 - \phi) \ex^r + \phi\, \ex^x \big)\,
  {1 + b \1(x < q) \over (K' + x)^{\beta + 1}} \,dx 
  - b \,u(\delta v) \,F_X(q) \,.\label{eq:pp}
\eeam
    {\red Is this worth a theorem?}
    {\blue No}
\begin{remark}\label{thrm:I}
 Assume the two-sided Pareto model \eqref{eq:pp} and that the utility \fct\ $u$ is increasing and differentiable. Then
$\frac{\pd \wt u_{\rm max}}{\pd \alpha} > 0$ and $\frac{\pd \wt u_{\rm max}}{\pd K} < 0$.
\end{remark}
The proof is given in Appendix~\ref{sec:thrmI_proof}. 
\par
We illustrate the results of remark~\ref{thrm:I} in Figure~\ref{fig:preference_pareto} for the power-utility
\fct\ \eqref{eq:u}.
For this reason, we replace $\phi$ in the first integral in \eqref{eq:pp} by the optimal $\hat\phi$. The resulting
quantity is denoted by $I(\alpha, K)$.
\par
We conclude that
$\wt u_{\rm max}$ increases with $\alpha$ and decreases with $K$. Therefore there is a curve of
equal preference on the $(\alpha, K)$-plane. Moving along this
curve in the direction of increasing $\alpha$, one expects the values
of $K$ to increase too, i.e., the estimated values of $\alpha$ and $K$
should appear positively dependent. This is indeed the case for some
real return data, e.g. the ``Energy'', ``Consumer Staples'' and
``Information Technology'' sectors of the S\&P 500 index; see 
Figure \ref{fig:sectors_parameters}. {\red how can I see positive dependence?}
\par
The value of $\hat\phi$ can be calculated
by numerical integration and optimization with respect to $\phi$ for given values of $K, K', \alpha, \beta$. 
This is shown in 
Figure \ref{fig:phi_hat_pareto} for the power utility \fct\ \eqref{eq:u}.
\begin{figure}
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto5e-1.pdf}    
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto4.pdf}
  \end{minipage}
  \caption{The graphs show $\hat\phi$, the optimal equity allocation
as a \fct\ of $\alpha$ and $K$ in the two-sided Pareto model \eqref{eq:pareto} with $K=K'$, $\alpha=\beta$. We choose
the utility $u$ from \eqref{eq:u}
    function $u(x) = -x^{-\xi}/\xi$ for $\xi = 1/2$
    (left) and $\xi = 4$ (right). {\rm change the $u(C)$ to $u(x)$ everywhere also in other figures, and use the same
structure of the formulas.}
  }
  \label{fig:phi_hat_pareto}
\end{figure}

@@

\begin{figure}[htb!]
  \centering
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Energy_alpha_K_ci.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Energy_p.pdf}
  \end{minipage}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Consumer_Staples_alpha_K_ci.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Consumer_Staples_p.pdf}
  \end{minipage}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Information_Technology_alpha_K_ci.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Information_Technology_p.pdf}
  \end{minipage}
  \caption{\small Estimates of $p$ and $K$ of stocks in sectors of the
    S\&P 500 index. The points are the estimated values; the bars are
    the $2\sigma$ confidence intervals. The confidence bands of the
    corresponding Hill estimates $\hat \alpha$ of these sectors are
    shown in figure~\ref{fig:1}.
  }
  \label{fig:sectors_parameters}
\end{figure}
To compare the maximum likelihood estimates with the results obtained
from Hill's scale estimates, one can re-write the lower-tail
distribution function: For all $x < 0$,
\begin{eqnarray*}
  \P(X < x)
  &=&
  p {K^\alpha \over (K - x)^\alpha} \\
  &=&
  p {K^\alpha |x|^{-\alpha} \over (1 - K/x)^\alpha} \\
  &=&
  p K^\alpha |x|^{-\alpha} \left(
  1 + {\alpha K \over x} + O(|x|^{-2})
  \right)
\end{eqnarray*}
% Comparing this expression with \eqref{eq:lower_tail_expansion},
Then one can identity $p K^\alpha$ as the scale parameter. Figure
\ref{fig:scale_estimates} compare the estimates obtained
from Hill's scale estimator with those from the $p K^\alpha$ method.

@@

\section{Proof of Theorem \ref{thrm:I}}
\label{sec:thrmI_proof}
\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \text{argmax}_{0 < \phi \leq 1} \mathcal U(F, \phi)
  \end{equation}
  We have
  \[
  G(F) = \mathcal U(F, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    {\pd G(F) \over \pd \alpha}
    &=&
    {\pd \mathcal U(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi)
    + {\pd \mathcal U(F, \phi) \over \pd \phi}(\alpha, K, \hat\phi)
    {\pd \hat\phi \over \pd \alpha}(\alpha, K)
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    {\pd \mathcal U(F, \phi) \over \pd \phi}(\alpha, K, \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    {\pd \mathcal U(F, \phi) \over \pd \alpha}(\alpha, K, \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    {\pd \mathcal U(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi)
    = {\partial \over \partial \alpha}\E[u((1 - \hat\phi) e^r + \hat\phi e^X) \1_{\{X < 0\}}]
  \end{eqnarray*}
  The function $u((1 - \hat\phi) e^r + \hat\phi e^X)$ is obviously
  increasing with $X$. It follows
  \begin{eqnarray*}
    && {\pd f(x; \alpha, K) \over \pd \alpha} \\
    &=& {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \ln\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    {\pd \mathcal U(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi) &>& 0
  \end{eqnarray*}
  As for ${\pd G(F) \over \pd K}$, by the same argument as for
  ${\pd G(F) \over \pd \alpha}$, it suffices to show
  \[
  {\pd \mathcal U(F, \phi) \over \pd K}(\alpha, K, \hat\phi) < 0
  \]
  We have
  \[
  {\pd \mathcal U(F, \phi) \over \pd K}(\alpha, K, \hat\phi)
  = {\partial \over \partial K} \E \left[
    u((1 - \hat\phi) e^r + \hat\phi e^X) \1_{\{X < 0\}}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && {\pd f(x; \alpha, K) \over \pd K} \\
    &=& {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  {\pd \mathcal U(F, \phi) \over \pd K}(\alpha, K, \hat\phi) < 0  
  \]
\end{proof}

>>>>

\subsection{Hill estimates of lower-tail scale parameters}\label{sec:HillScaleEstimates}
We assume the pure Pareto model \eqref{eq:3} with scale parameter $K>0$.
Hill \cite{hill1975simple} proposed  the maximum-likelihood estimator of $K$
derived from the joint \ds\ of $k$ upper order statistics in the sample; cf.
Embrechts et al. \cite{embrechts:klueppelberg:mikosch:1997}, p.~334.
It is given by
\beao
\hat K_k = \left({k \over n}\right)^{1/\hat\alpha} X_{(n-k)}\,.
\eeao
Using the asymptotic normality property of upper order statistics
(cf. de Haan and Ferreira~\cite{haan:ferreira:2006}, theorem 2.2.1), one can show
\begin{eqnarray*}
  \sqrt k (\hat K_k - K) &\overset{d}{\to}& N\left(
    0, \left( {K \over \alpha}  \right)^2
  \right) \\
  \sqrt k (\hat K_k^\alpha - K^\alpha) &\overset{d}{\to}& N\left(
    0, \left( {K^{2\alpha}}  \right)^2
  \right)
\end{eqnarray*}
where the tail index $\alpha$ is regarded as known. From the above
asymptotic normality property, confidence bands of the estimate of $K$
and $K^\alpha$ can be constructed. 
Estimates of $K$ of the ``Energy'', ``Consumer Staples'' and
``Information Technology'' sectors of the S\&P 500 index are computed
using this method. The results are shown in
Figure~\ref{fig:sectors_parameters}.
One can see that $K$ generally takes a rather small value. For the
more volatile sectors of ``Energy'' and ``Information Technology'',
the average value of $K$ is around 0.01, while for the more stable
sector of ``Consumer Staples'', the average value is around 0.005. Due
to the smallness of $K$, mild variations of $\alpha$ would lead to
huge variations of $K^\alpha$, as shown in the 2nd column of
figure~\ref{fig:sectors_parameters}.

Secondly, one can see that the values of $\alpha$ and $K$ are appear
positively correlated. This prompts Pareto tails of the return
distributions. We expain more about this in
section~\ref{sec:pareto_tail}.

\subsection{A test of equal tail indices based on Hill estimator}
From \eqref{eq:2} one can deduce
\begin{equation}
  \label{eq:x1}
  \sqrt k (\hat \alpha_A - \hat \alpha_B) \overset{d}{\to} N(0, \alpha_A^2 - \alpha_B^2)  
\end{equation}
where $\hat \alpha_A$ and $\hat \alpha_B$ are Hill estimates of
$\alpha_A$ and $\alpha_B$, the tail indices of two series $A$ and
$B$. The weak convergence of \eqref{eq:x1} allows one to construct a
test of the equality of $\alpha_A$ and $\alpha_B$.

@@

\subsection{Pareto-distributed returns}\label{sec:pareto_tail}
We consider the case when $X$ has a two-sided Pareto \ds\ given by
\beam\label{eq:pareto}
  F_X(x) = \left\{
  \begin{array}{ll}
    p \left(
    {K \over K - x}
    \right)^\alpha & x \leq 0 \,,\\
    1 - (1 - p) \left(
    {K' \over K' + x}
    \right)^\beta & x > 0\,,
  \end{array}
  \right.
\eeam
where 
$\alpha, \beta > 1$, $0 < p < 1$ and $K,K' > 0$. Then we have
\beam\label{eq:xxie1.0}
 \wt u(F_X,\phi)\nonumber
  &=&
  \alpha\, K^\alpha\,  p\,
  \int_{-\infty}^0
  u\big( (1 - \phi) \ex^r + \phi \ex^x \big)\,
  {1 + b \over (K - x)^{\alpha + 1}} \,dx\\
    &&+
  \beta \,(K')^\beta\, (1 - p)
  \int_{0}^\infty
  u\big( (1 - \phi) \ex^r + \phi\, \ex^x \big)\,
  {1 + b \1(x < q) \over (K' + x)^{\beta + 1}} \,dx 
  - b \,u(\delta v) \,F_X(q) \,.\label{eq:pp}
\eeam
    {\red Is this worth a theorem?}
    {\blue No}
\begin{remark}\label{thrm:I}
 Assume the two-sided Pareto model \eqref{eq:pp} and that the utility \fct\ $u$ is increasing and differentiable. Then
$\frac{\pd \wt u_{\rm max}}{\pd \alpha} > 0$ and $\frac{\pd \wt u_{\rm max}}{\pd K} < 0$.
\end{remark}
The proof is given in Appendix~\ref{sec:thrmI_proof}. 
\par
We illustrate the results of remark~\ref{thrm:I} in Figure~\ref{fig:preference_pareto} for the power-utility
\fct\ \eqref{eq:u}.
For this reason, we replace $\phi$ in the first integral in \eqref{eq:pp} by the optimal $\hat\phi$. The resulting
quantity is denoted by $I(\alpha, K)$.
\par
We conclude that
$\wt u_{\rm max}$ increases with $\alpha$ and decreases with $K$. Therefore there is a curve of
equal preference on the $(\alpha, K)$-plane. Moving along this
curve in the direction of increasing $\alpha$, one expects the values
of $K$ to increase too, i.e., the estimated values of $\alpha$ and $K$
should appear positively dependent. This is indeed the case for some
real return data, e.g. the ``Energy'', ``Consumer Staples'' and
``Information Technology'' sectors of the S\&P 500 index; see 
Figure \ref{fig:sectors_parameters}.
\par
The value of $\hat\phi$ can be calculated
by numerical integration and optimization with respect to $\phi$ for given values of $K, K', \alpha, \beta$. 
This is shown in 
Figure \ref{fig:phi_hat_pareto} for the power utility \fct\ \eqref{eq:u}.
\begin{figure}
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto5e-1.pdf}    
  \end{minipage}\hfill
  \begin{minipage}{0.5\linewidth}
    \includegraphics[width=\textwidth]{phi_hat_pareto4.pdf}
  \end{minipage}
  \caption{The graphs show $\hat\phi$, the optimal equity allocation
    as a \fct\ of $\alpha$ and $K$ in the two-sided Pareto model
    \eqref{eq:pareto} with $K=K'$, $\alpha=\beta$. We choose
    the utility $u$ from \eqref{eq:u}
    function $u(x) = -x^{-\xi}/\xi$ for $\xi = 1/2$ (left) and $\xi = 4$
    (right). {\rm change the $u(C)$ to $u(x)$ everywhere also in other
      figures, and use the same structure of the formulas.}
  }
  \label{fig:phi_hat_pareto}
\end{figure}

@@

\begin{figure}[htb!]
  \centering
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Energy_K.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Energy_scale.pdf}
  \end{minipage}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Consumer_Staples_K.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Consumer_Staples_scale.pdf}
  \end{minipage}
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Information_Technology_K.pdf}
  \end{minipage}\hfill
  \begin{minipage}{0.45\linewidth}
    \includegraphics[width=\textwidth]
    {Information_Technology_scale.pdf}
  \end{minipage}
  \caption{\small Estimates of $K$ and $K^\alpha$ of stocks in sectors
    of the S\&P 500 index. The points are the estimated values; the bars are
    the $2\sigma$ confidence intervals. The confidence bands of the
    corresponding Hill estimates $\hat \alpha$ of these sectors are
    shown in figure~\ref{fig:1}. Note $\log_{10}(K^\alpha)$ is shown
    instead of $K^\alpha$.
  }
  \label{fig:sectors_parameters}
\end{figure}
To compare the maximum likelihood estimates with the results obtained
from Hill's scale estimates, one can re-write the lower-tail
distribution function: For all $x < 0$,
\begin{eqnarray*}
  \P(X < x)
  &=&
  p {K^\alpha \over (K - x)^\alpha} \\
  &=&
  p {K^\alpha |x|^{-\alpha} \over (1 - K/x)^\alpha} \\
  &=&
  p K^\alpha |x|^{-\alpha} \left(
  1 + {\alpha K \over x} + O(|x|^{-2})
  \right)
\end{eqnarray*}
% Comparing this expression with \eqref{eq:lower_tail_expansion},
Then one can identity $p K^\alpha$ as the scale parameter. Figure
\ref{fig:scale_estimates} compare the estimates obtained
from Hill's scale estimator with those from the $p K^\alpha$ method.

@@

\section{Proof of Remark \ref{thrm:I}}
\label{sec:thrmI_proof}
\begin{proof}
  Let
  \begin{equation}
    \label{eq:xxie2}
    \hat \phi := \text{argmax}_{0 < \phi \leq 1} \mathcal U(F, \phi)
  \end{equation}
  We have
  \[
  G(F) = \mathcal U(F, \hat\phi)
  \]
  It follows
  \begin{eqnarray}
    {\pd G(F) \over \pd \alpha}
    &=&
    {\pd \mathcal U(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi)
    + {\pd \mathcal U(F, \phi) \over \pd \phi}(\alpha, K, \hat\phi)
    {\pd \hat\phi \over \pd \alpha}(\alpha, K)
    \label{eq:xxie3}
  \end{eqnarray}
  The definition \eqref{eq:xxie2} implies $\forall \alpha > 1$
  \begin{equation}
    \label{eq:xxie4}
    {\pd \mathcal U(F, \phi) \over \pd \phi}(\alpha, K, \hat \phi) = 0
  \end{equation}
  So the second term of \eqref{eq:xxie3} vanishes. It remains to show
  \begin{eqnarray*}
    {\pd \mathcal U(F, \phi) \over \pd \alpha}(\alpha, K, \hat \phi)
    &>& 0
  \end{eqnarray*}
  From \eqref{eq:xxie1.0}, it follows
  \begin{eqnarray*}
    {\pd \mathcal U(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi)
    = {\partial \over \partial \alpha}\E[u((1 - \hat\phi) e^r + \hat\phi e^X) \1_{\{X < 0\}}]
  \end{eqnarray*}
  The function $u((1 - \hat\phi) e^r + \hat\phi e^X)$ is obviously
  increasing with $X$. It follows
  \begin{eqnarray*}
    && {\pd f(x; \alpha, K) \over \pd \alpha} \\
    &=& {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    - {K^\alpha \over (K - x)^{\alpha + 1}}
    \left[
      \alpha
      \ln\left(
        1 - {x \over K}
      \right) - 1
    \right]
  \end{eqnarray*}
  It is easily checked that when $x < K(1 - e^{1/\alpha}) < 0$,
  \[
  {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  and when $K(1 - e^{1/\alpha}) < x < 0$,
  \[
  {\partial \over \partial \alpha} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  This is the second case of lemma \ref{lemma:I}. So we have
  \begin{eqnarray*}
    {\pd \mathcal U(F, \phi) \over \pd \alpha}(\alpha, K, \hat\phi) &>& 0
  \end{eqnarray*}
  As for ${\pd G(F) \over \pd K}$, by the same argument as for
  ${\pd G(F) \over \pd \alpha}$, it suffices to show
  \[
  {\pd \mathcal U(F, \phi) \over \pd K}(\alpha, K, \hat\phi) < 0
  \]
  We have
  \[
  {\pd \mathcal U(F, \phi) \over \pd K}(\alpha, K, \hat\phi)
  = {\partial \over \partial K} \E \left[
    u((1 - \hat\phi) e^r + \hat\phi e^X) \1_{\{X < 0\}}
  \right] 
  \]
  and
  \begin{eqnarray*}
    && {\pd f(x; \alpha, K) \over \pd K} \\
    &=& {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} \\
    &=&
    -\alpha K^{\alpha - 1} {
      \alpha x + K
      \over
      (K - x)^{\alpha + 2}
    }
  \end{eqnarray*}
  Clearly, when $x < -\alpha/K$
  \[
  {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} > 0
  \]
  and when $-\alpha/K < x < 0$
  \[
  {\partial \over \partial K} {\alpha K^\alpha \over (K - x)^{\alpha + 1}} < 0
  \]
  So by the 1st case of remark \ref{remark:I} we conclude
  \[
  {\pd \mathcal U(F, \phi) \over \pd K}(\alpha, K, \hat\phi) < 0  
  \]
\end{proof}
